---
title: "A Social Web Analysis of EA SPORTS FC 27 Launch Discourse on YouTube"
author: "Amansingh Bhatia, Suwaid Begg, Avinay Nand"
output:
  pdf_document:
    toc: false
    number_sections: false
fontsize: 10pt
geometry: margin=0.65in
header-includes:
  - \usepackage{setspace}
  - \setstretch{0.95}
editor_options:
  markdown:
    wrap: 72
---

```{r setup, include=FALSE}
# making sure the output style is looking the same everywhere
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  collapse = TRUE,
  fig.align = "center",
  fig.width = 7,
  fig.height = 4.5
)

# loading just the packages we are using for the next few parts
library(jsonlite)
library(tm)
library(SnowballC)
library(wordcloud)

# pulling in the saved data so we are working with the same files for everything
selected_videos = read.csv("data_raw/selected_videos.csv", stringsAsFactors = FALSE)
top_comments = read.csv("data_raw/fc27_top_level_comments_72h.csv", stringsAsFactors = FALSE)
replies = read.csv("data_raw/fc27_replies_72h.csv", stringsAsFactors = FALSE)
analysis_comments = read.csv("data_clean/fc27_comments_720.csv", stringsAsFactors = FALSE)
collection_summary = read.csv("data_clean/collection_summary.csv", stringsAsFactors = FALSE)
```

# 1. Investigation Overview

This report investigates early EA SPORTS FC 27 launch discourse on
YouTube using content and interaction analysis. Instead of considering
all FC 27 comments together, we focused on comparing three kinds of
content created by creators: Review / First Impressions, Ultimate Team
and Career Mode.

The research question of the project is:

> **What is the structure of early FC 27 launch discourse in different
> categories of YouTube videos, and how does this discourse get
> organised in terms of user interaction**?

The research design is guided by four closely related research
questions:

-   **Interaction**: Is there any sort of relationship that can be seen
    between the category of a video and how people reply to a top-level
    comment in 72 hours?

-   **Text/content**: What kinds of words and text patterns can be found
    in the comments and how do these words and patterns differ from one
    category to another?

-   **Clustering**: Can comments be grouped into clusters based on
    textual features, this means can they be categorized in some way?

-   **Network**: How is the network of replies structured and who are
    considered to be important users in that network?

All these stages are supposed to come together and provide one
comprehensive investigation of the phenomenon being studied. In
hypothesis testing, the first step would be to determine if there are
any differences in the interaction levels among different types of
content. Afterwards, in the text analysis stage, it would be necessary
to identify what topics users are discussing, and clustering should
reveal whether or not there are meaningful groups of texts without
actually using the category labels for that purpose.

# 2.1. Data Collection

This study examines early discussions on YouTube regarding EA SPORTS FC
27. We analysed three types of FC 27 videos: Reviews or First
Impressions, Ultimate Team, and Career Mode. We selected three videos
from each category, resulting in a total of nine videos.

Initially, we screened candidate videos to determine which ones would
form the dataset. The selected videos needed to be relevant to FC 27,
fit into one of the three chosen categories, be in English, and be
produced by individual creators rather than EA. It was essential to
include different creators in each category and to ensure that the full
72 hours for observation were available. Additionally, we required
adequate comments from early viewers to achieve a balanced sample.

To enhance the comparability of the videos, we retained only the
comments and replies made within the first 72 hours following the
release of each video. Without this defined timeframe, older videos
could accumulate more comments, while newer videos would not have the
same opportunity. We collected the data using the YouTube Data API in R,
employing the jsonlite package to read JSON replies.

The entire data collection process is outlined in R/01_collect_data.R.
We used the Youtube commentThreads endpoint to gather pages of top-level
comments, continuing until all nextPageTokens were used. We collected
all top-level comments along with their replies via the comments API by
employing the top-level comment ID as the parent ID. The publish dates
of the top-level comments and their replies were then compared within a
72-hour timeframe.

The following important top-level variables were collected: videoId,
commentId, authorDisplayName and authorChannelId, commentText, likes,
publicationTime and replyCount. Among the reply variables, the following
data were collected: replyId, parentCommentId, parentAuthorDisplayName
and authorDisplayName, parentChannelId and authorChannelId, replyText,
likes, publicationTime. Furthermore, details about creator, video title
and analytical category were provided.

```{r api-example, eval=FALSE}
# keeping the api key saved in a different file so it's not showing up in the code we are handing in
source("api_key.R")

videoId = selected_videos$videoId[1]

url = paste0(
  "https://www.googleapis.com/youtube/v3/commentThreads",
  "?part=snippet&videoId=", videoId,
  "&maxResults=100&order=time&key=", youtube.api.key
)

# getting the first page, but the main script is following the next page token until we are getting all the pages
example_request = fromJSON(url)
```

The final dataset has 1,388 unique top-level comments and 480 unique
replies. For Sections 2.2, 2.3, and 2.4, 80 top-level comments from
every video, which is nine videos in total, are picked randomly and with
a set seed. This leads to a total of 720 balanced comments which
consists of 240 comments in each of the three categories. In Section
2.5, all the replies from the dataset are used.

```{r data-summary}
# putting together a table showing the total amount of data we are looking at
data.frame(
  Measure = c(
    "Selected videos",
    "Unique top-level comments",
    "Unique replies",
    "Balanced analysis comments"
  ),
  # counting up the rows in our datasets to get the final numbers for each part
  Total = c(
    nrow(selected_videos),
    nrow(top_comments),
    nrow(replies),
    nrow(analysis_comments)
  )
); 
```

There was a lot of variation in how much natural discussion occurred, so
there’s a need to balance the analysis sample to make sure that the
bigger videos don’t overshadow the hypothesis and the text and cluster
analysis that follows.

```{r collection-table}
# making a table showing each creator we are looking at
knitr::kable(
  collection_summary[, c(
    "category",
    "creator",
    # pulling the columns showing their natural activity over the first 72 hours
    "topLevelComments72h",
    "sampledComments",
    "replies72h"
  )],
  # renaming the headings here so the table is reading clearly for the assignment
  col.names = c(
    "Category",
    "Creator",
    "Top-level comments",
    "Sampled",
    "Replies"
  ),
  caption = "Selected videos and data collected in the first 72 hours"
)
```

For the final data quality check, we examined duplicate comment and
reply IDs prior to analysis.

```{r collection-checks}


# checking our data one last time for any duplicates
c(
  duplicate_comments = sum(duplicated(top_comments$commentId)),
  # making sure both of these numbers are coming out as zero
  duplicate_replies = sum(duplicated(replies$replyId))
)
```

Final files did not have any duplicate IDs. The collection table shows
that any video that was collected gave 80 comments to the balanced
sample, which is something to note.

There are some restrictions that apply to this collection. The nine
videos are not a random selection of all of the FC 27 videos, because
they were picked on purpose, and the discussion about the videos can
vary by individual makers. The 72-hour window is focused on the initial
reactions to the launch and it doesn't really include any later
discussion. Also, it’s important to mention that YouTube commenters are
a self-selected group, so the results from this should not be seen as a
true survey of all FC 27 players or anything like that.

# 2.2 Hypothesis Testing

The first analytical question is:

> **Is video category associated with whether a sampled top-level
> comment receives at least one reply within the first 72 hours?**

This question adds an interaction measure to the comparison between
Review, Ultimate Team and Career Mode videos.

The hypotheses are:

$$
H_0:\text{ Video category and reply status are independent.}
$$

$$
H_A:\text{ Video category and reply status are associated.}
$$

A comment is considered to have received a reply if its comment ID is
listed as a parent comment in the 72-hour reply dataset.

```{r reply-status}
# checking if the comments we sampled are showing up in the 72-hour reply file
analysis_comments$receivedReply72h = ifelse(
  analysis_comments$commentId %in% unique(replies$parentCommentId),
  "At least one reply",
  "No replies"
)

# making sure our categories are reading in the right order for the assignment
analysis_comments$category = factor(
  analysis_comments$category,
  levels = c("Review", "Ultimate Team", "Career Mode")
)

# setting up the reply status as a factor so the table is looking clean
analysis_comments$receivedReply72h = factor(
  analysis_comments$receivedReply72h,
  levels = c("No replies", "At least one reply")
)

# putting together a table to see the actual counts
reply_table = table(
  analysis_comments$category,
  analysis_comments$receivedReply72h
)

reply_table
# calculating the proportions for each category based on the table we just made
round(prop.table(reply_table, 1), 3)
```

The "Review" category received the highest reply rate at 19.6%, followed
by "Ultimate Team" at 13.3%, and "Career Mode" at 10.8%.

Given that there are only nine videos available for comments, we also
calculated the response rate for each individual video. This approach
assists in identifying whether the overall reply rate for each category
is influenced by any specific creator.

```{r reply-rate-by-video}
# turning the reply status into numbers so we are able to add them up easily
analysis_comments$receivedReplyNumber = ifelse(
  analysis_comments$receivedReply72h == "At least one reply",
  1,
  0
)

# below we are grouping everything by video and creator to see how many replies each one is getting
reply_by_video = aggregate(
  receivedReplyNumber ~ videoId + category + creator,
  data = analysis_comments,
  FUN = sum
)

names(reply_by_video)[4] = "CommentsWithReply"
# working out the percentage since we are knowing each video is giving us exactly 80 sampled comments
reply_by_video$ReplyRatePercent = round(
  100 * reply_by_video$CommentsWithReply / 80,
  1
)

# sorting the rows so the categories are showing up in the correct order for the report
reply_by_video = reply_by_video[
  order(
    factor(
      reply_by_video$category,
      levels = c("Review", "Ultimate Team", "Career Mode")
    ),
    reply_by_video$creator
  ),
]

# building the final latex table to show the reply rates for the nine videos
knitr::kable(
  reply_by_video[, c(
    "category",
    "creator",
    "CommentsWithReply",
    "ReplyRatePercent"
  )],
  col.names = c(
    "Category",
    "Creator",
    "Comments with reply",
    "Reply rate (%)"
  ),
  row.names = FALSE,
  caption = "Reply rates within the nine selected videos",
  format = "latex",
  booktabs = TRUE,
  longtable = FALSE
)
```

The three Review videos were quite similar at 18.8% to 20.0%. Ultimate
Team varied from 10.0% to 16.2%. Career mode had more varied results;
BFordLancer was at 18.8% compared to CaniSports which was at 7.5% and
Mark Goldbridge at 6.2%. The variation is important in the
interpretation of the test.

Since both variables were categorical, a Pearson chi-square test of
independence was performed. variables were categorical, Pearson
chi-square test for independence was performed. This examines if the
observed numbers differ from the counts that we predict assuming video
category and reply status are independent.

```{r chi-square}
# running the chi-square test we are covering in COMP3020
reply_test = chisq.test(reply_table)

# showing the main results here so we are seeing how it went
reply_test

# checking our expected numbers to make sure they are looking okay
round(reply_test$expected, 2)

# finding the smallest expected value just to make sure everything is working right
min(reply_test$expected)
```

The test produced a statistic of $\chi^2(2) = 7.8272$ with a p-value of
0.01997. Since the p-value is below 0.05, we reject the null hypothesis
(H0). This indicates that there is a relationship between video type and
the likelihood of receiving at least one reply to comments. The test
assesses the overall association across three categories but does not
confirm that all pairs of categories differ.

All expected cell frequencies were at least 35, validating the use of
the conventional chi-square approximation. Under the assumption of
independence, 35 comments with at least one reply would be expected in
each category. Review had 47 comments with at least one reply, while
Career Mode had 26, which contributes to the observed disparity.

This suggests a relationship rather than a direct cause-and-effect link.
Because comments are nested within nine selected videos, the
independence assumption may not hold perfectly. Therefore, the results
of the chi-square test should be interpreted as indicative of a
relationship among these specific launch comments.

# 2.3 Text and Content Analysis

The next question is:

> **What words and textual patterns characterise the comments, and how
> do these patterns differ across the three video categories?**

## Text cleaning

The balanced dataset contained 720 non-missing, non-blank comments.

```{r text-check}
# checking for any missing comments before we are starting to build the text corpus
c(
  comments = nrow(analysis_comments),
  missing = sum(is.na(analysis_comments$commentText)),
  # counting up the blank ones here just to be sure the data is looking clean
  blank = sum(trimws(analysis_comments$commentText) == "")
)
```

The comments were compiled into a corpus. We removed URLs, digits,
punctuation, and common English stop words, converting all words to
lower case.

Additionally, we used a small custom set of stop words. This mainly
filtered out dataset labels, creator names, and generic conversational
terms that appeared frequently but were not helpful in distinguishing
discussion topics.

```{r corpus}
# fixing up any empty comments first so they are not breaking the code
analysis_comments$commentText[is.na(analysis_comments$commentText)] = ""

# building the main text corpus where we are treating every youtube comment as its own document
comments.corpus = Corpus(VectorSource(analysis_comments$commentText))

# converting the text to ascii which is dropping all the emojis from the comments
comments.corpus = tm_map(
  comments.corpus,
  function(x) iconv(x, to = "ASCII", sub = " ")
)

# setting up a function for removing any web links people are posting
remove_urls = content_transformer(function(x) {
  gsub("https?://\\S+|www\\.\\S+", " ", x, perl = TRUE)
})

# actually taking the urls out of the text now
comments.corpus = tm_map(comments.corpus, remove_urls)

# doing some basic cleaning here like taking out the numbers and punctuation
comments.corpus = tm_map(comments.corpus, removeNumbers)
comments.corpus = tm_map(comments.corpus, removePunctuation)

# making everything lowercase and getting rid of the extra spaces
comments.corpus = tm_map(comments.corpus, stripWhitespace)
comments.corpus = tm_map(comments.corpus, tolower)

# making a list of custom stop words so we are filtering out game names and creators that are taking over our word counts
custom_words = c(
  "fc", "fc27", "eafc", "ea", "sports",
  "game", "like", "just", "get", "got", "can",
  "will", "even", "much", "still", "now", "one",
  "video", "really", "back",
  "dont", "cant", "ive", "im", "thats", "youre",
  "yeah", "bro",
  "gamingbolt", "inception", "machete",
  "auziomf", "auzio", "aa9skillz", "skillz",
  "nepenthez", "nep", "canisports", "cani",
  "mark", "goldbridge", "bfordlancer", "bford"
)

# removing the standard stop words and our custom list from the text
comments.corpus = tm_map(
  comments.corpus,
  removeWords,
  c(stopwords(), custom_words)
)

# stripping the extra spaces one more time so the text is looking nice and neat
comments.corpus = tm_map(comments.corpus, stripWhitespace)
```

## Overall word frequencies

We created a term-document matrix from the cleaned corpus. Then, we
calculated the total frequency of each term across all 720 comments.

```{r frequency-matrix}
# building the term document matrix here so we are ready to analyze the text
comments.tdm = TermDocumentMatrix(comments.corpus)
comments.matrix = as.matrix(comments.tdm)

# counting up how often each term is showing up in our data
term_frequency = sort(rowSums(comments.matrix), decreasing = TRUE)

# looking at the 20 most common words we are finding
head(term_frequency, 20)
```

Each category contains an equal number of comments, thus eliminating one
possible source of imbalance. However, the comments could vary in terms
of their number of words. To make it easier to compare the data
visually, we normalized the frequency of each term with the total number
of cleaned terms in each category.

```{r overall-wordcloud, fig.width=6.5, fig.height=3.2, out.width='60%'}
# setting the seed here so we are getting the exact same word cloud every time
set.seed(3020)

# building the actual word cloud for the words that are showing up at least 5 times
wordcloud(
  words = names(term_frequency),
  freq = term_frequency,
  min.freq = 5,
  # limiting this to 80 words so the plot is not looking too messy for the report
  max.words = 80,
  random.order = FALSE
)
```

The word cloud is a global look of vocabulary. It also shows more
specific phrases such as evos, pack, market, chelsea and passing showing
that the merged dataset comprises multiple separate conversation themes.

## Comparison of the three categories

Each category has the same number of comments, so that removes one cause
of imbalance, but the comments themselves can have varied numbers of
words. To allow for a truer visual comparison, each term count was
consequently divided by the total number of cleaned term occurrences in
that category.

```{r category-frequencies}
# counting up the words for the review videos
review_counts = rowSums(
  comments.matrix[, analysis_comments$category == "Review", drop = FALSE]
)

# doing the same counting for the ultimate team ones
ultimate_counts = rowSums(
  comments.matrix[, analysis_comments$category == "Ultimate Team", drop = FALSE]
)

# and counting the words for the career mode category
career_counts = rowSums(
  comments.matrix[, analysis_comments$category == "Career Mode", drop = FALSE]
)

# turning these counts into percentages so we are able to compare the categories fairly
review_relative = sort(
  100 * review_counts / sum(review_counts),
  decreasing = TRUE
)

# sorting the ultimate team percentages from highest to lowest
ultimate_relative = sort(
  100 * ultimate_counts / sum(ultimate_counts),
  decreasing = TRUE
)

# getting the career mode percentages sorted out too
career_relative = sort(
  100 * career_counts / sum(career_counts),
  decreasing = TRUE
)

# looking at the top 10 words for the review videos
head(review_relative, 10)
# checking the top 10 for ultimate team
head(ultimate_relative, 10)
# and seeing the top 10 for career mode
head(career_relative, 10)
```

The most frequent terms include `play`, `fifa`, `year`, `player`,
`team`, `mode`, `football`, `career` and `gameplay`, showing that
discussion centres on gameplay, players and game modes. More specialised
terms such as `evos`, `pack`, `market`, `chelsea` and `passing` indicate
several narrower discussion themes.

```{r category-plots, fig.width=9, fig.height=3.5, out.width='100%'}
# pulling the top 10 words for each of our three categories
review_top = head(review_relative, 10)
ultimate_top = head(ultimate_relative, 10)
career_top = head(career_relative, 10)

# finding the highest number across all three so we are setting the same axis limit for a fair comparison
common_max = max(review_top, ultimate_top, career_top)

# setting up the layout so we are showing all three graphs side by side
par(mfrow = c(1, 3), mar = c(4, 7, 3, 1))

# building the bar chart for the review category first
barplot(
  rev(review_top),
  horiz = TRUE,
  las = 1,
  main = "Review",
  xlab = "% of cleaned term occurrences",
  xlim = c(0, common_max * 1.05),
  cex.names = 0.8
)

# making the second bar chart for the ultimate team words
barplot(
  rev(ultimate_top),
  horiz = TRUE,
  las = 1,
  main = "Ultimate Team",
  xlab = "% of cleaned term occurrences",
  xlim = c(0, common_max * 1.05),
  cex.names = 0.8
)

# putting together the last bar chart for career mode
barplot(
  rev(career_top),
  horiz = TRUE,
  las = 1,
  main = "Career Mode",
  xlab = "% of cleaned term occurrences",
  xlim = c(0, common_max * 1.05),
  cex.names = 0.8
)

# resetting the plot layout back to normal so we are not messing up any future graphs
par(mfrow = c(1, 1))
```

Category patterns remain identifiable even when controlling for the
amount of cleaned text. The review conversation is more general,
Ultimate Team has the most specific mode language, and Career Mode has
identifiable career-related phrases. However, some terms like player or
club names can also be an artefact of the specific creators and videos
selected, thus these patterns should not be seen as pure category
effects.

## TF-IDF weighting

Raw frequency shows common words. The cleaned corpus was stemmed and
weighted using TF-IDF to provide a representation that assigns more
weight to terms that are distinctive in the individual comments.

```{r tfidf}
# stemming the words here so we are counting related forms together like turning playing into play
stemmed.corpus = tm_map(comments.corpus, stemDocument)

# making a new term document matrix for these stemmed words
stemmed.tdm = TermDocumentMatrix(stemmed.corpus)

# applying the tf-idf weighting which is downweighting the words that are showing up in too many comments
stemmed.tfidf = weightTfIdf(stemmed.tdm)

# converting this into a matrix format so we are able to work with the numbers
tfidf.matrix = as.matrix(stemmed.tfidf)

# adding up and sorting the terms by their total weight from highest to lowest
tfidf_term_weight = sort(rowSums(tfidf.matrix), decreasing = TRUE)

# pulling up the top 15 terms so we are seeing what is most important based on the weights
head(tfidf_term_weight, 15)
```

The most weighted total TF-IDF words included more particular words such
as pepe, lucio, pack, goat, fifa and look. Herein lies the ability of
TF-IDF to identify unique names and language related to a particular
mode rather than through mere frequency. Here we see that frequency
analysis accounts for what is common throughout the sample, while TF-IDF
helps in identifying unique terms.

Word-level processing has its drawbacks. The word analysis method
doesn't preserve the meaning of the sentence, sarcasm, or context. The
custom stop-word list involves judgement. Ascii coding eliminates emojis
and some special characters. Words related to a particular player, club
or creator may reflect one selected video rather than the whole
category. It would be fair to see the obtained results as the general
vocabulary tendencies, not the complete interpretation of the intentions
of each commentator.

# 2.4 Clustering

The final question in this part of the report is: **Can the comments be
grouped into meaningful clusters based on their textual content?**

Since we used the clustering process using the TF-IDF vector of Section
2.3, therefore clustering results are a direct output of the previous
text analysis.

## Preparing the document vectors

In order to do clustering the comments had to be rows and terms had to
be columns. Comments that became completely empty after preprocessing
were removed because they contain no terms that can be compared.

```{r clustering-data}
# flipping the matrix around so each row is a single comment
clustering.matrix = t(tfidf.matrix)

# figuring out which comments are completely empty now
empty_documents = which(rowSums(abs(clustering.matrix)) == 0)

# checking how many empty ones we got
length(empty_documents)

# taking out those empty comments from our main matrix
clustering.matrix = clustering.matrix[-empty_documents, ]

# keeping the category labels for the comments we are saving so we can look at them later
cluster_categories = analysis_comments$category[-empty_documents]

# just looking at the final size and seeing what categories we have left
dim(clustering.matrix)
table(cluster_categories)
```

After we had processed the data for clustering, 19 comments had become
empty and we used 701 comments for clustering.

Text documents showed variability in length and are often sparse. We
utilised cosine distance, ensuring that the TF-IDF vectors were
normalised to unit length, in accordance with the clustering techniques.
For unit vectors, the cosine distance corresponds to half the squared
Euclidean distance.

Since K-means operates in Euclidean space, we used Multidimensional
Scaling (MDS) to convert the cosine distances into Euclidean space.

```{r cosine-mds}
# Normalising the TF-IDF vectors so they all have a length of one
norm.matrix = diag(
  1 / sqrt(rowSums(clustering.matrix^2))
) %*% clustering.matrix

# Converting those euclidean distances into cosine distances
D = dist(norm.matrix, method = "euclidean")^2 / 2

N = nrow(clustering.matrix)

# Using almost all the dimensions for the clustering step
mds.matrix = cmdscale(D, k = N - 1)

# Keeping only two dimensions for the plot
mds2.matrix = cmdscale(D, k = 2)
```

The high-dimensional MDS representation is used for clustering. The
separate two-dimensional representation is used only for visualisation.

## Choosing the number of clusters

The elbow method was used to examine solutions from 1 to 15 clusters.

```{r elbow, fig.width=6.5, fig.height=3.8, out.width='78%'}
# Checking the number of clusters from 1 to 15 using the within-cluster sum of squares.
set.seed(3020)

# Creating a vector to store the sum of squares for each cluster count.
SSW = rep(0, 15)

# Running k-means for each number of clusters.
# Using nstart = 20 to reduce the effect of random starting points.
for (k in 1:15) {
  K = kmeans(mds.matrix, centers = k, nstart = 20)
  SSW[k] = K$tot.withinss
}

# Plotting the results to see where the decrease in the sum of squares starts slowing down.
plot(
  1:15,
  SSW,
  type = "b",
  xlab = "Number of clusters",
  ylab = "Within-cluster sum of squares",
  main = "Elbow method"
)
```

The elbow curve gradually declines instead of indicating a single
optimal value. Therefore, we compared the nearby solutions of *2, 3, 4,
and 5 clusters* instead of selecting $k$ based solely on the graph.

```{r compare-k}
# Setting the same seed before each run to keep the results consistent.
set.seed(3020)
K2 = kmeans(mds.matrix, centers = 2, nstart = 20)

# Running k-means again with 3 clusters.
set.seed(3020)
K3 = kmeans(mds.matrix, centers = 3, nstart = 20)

# Trying the same process with 4 clusters.
set.seed(3020)
K4 = kmeans(mds.matrix, centers = 4, nstart = 20)

# Checking one more solution using 5 clusters.
set.seed(3020)
K5 = kmeans(mds.matrix, centers = 5, nstart = 20)

# Creating a table to compare the cluster sizes for each solution.
cluster_sizes = data.frame(
  Solution = c("k = 2", "k = 3", "k = 4", "k = 5"),
  Sizes = c(
    paste(sort(table(K2$cluster), decreasing = TRUE), collapse = ", "),
    paste(sort(table(K3$cluster), decreasing = TRUE), collapse = ", "),
    paste(sort(table(K4$cluster), decreasing = TRUE), collapse = ", "),
    paste(sort(table(K5$cluster), decreasing = TRUE), collapse = ", ")
  )
)

# Displaying the cluster sizes to see how the observations are being divided.
knitr::kable(
  cluster_sizes,
  caption = "Cluster sizes for the candidate solutions"
)
```

In the analysis of the two-cluster, we observed that the resulting
clusters comprised **621 and 80 comments** respectively. Within these
clusters, the smaller cluster contained **63.7% Review** content,
whereas the larger cluster of 621 comments showed a more balanced
distribution across the three categories. The most significant keywords
identified in this smaller cluster included general Review and gameplay
terms such as `fifa`, `look`, and `year`, so $k=2$ did not separate the
distinctive Ultimate Team pack discussion.

```{r k2-check}
# Checking how the different categories are being grouped in the 2-cluster solution.
round(
  prop.table(
    table(K2$cluster, cluster_categories),
    1
  ),
  3
)
```

With the 3-cluster solution, there were **534, 145, and 22 comments** in
each cluster. The additional cluster represents a small but distinctive
group of Ultimate Team pack comments, while the 145-comment
Review/gameplay group also remains interpretable.

For that reason, **three clusters were chosen**. This choice was made
taking into account the shape of the elbow together with the structure
and interpretation of $k=2,3,4,5$, and not the fact that there were
three video categories in the initial dataset.

## Interpretation of three clusters

The video categories were not used in the clustering process. They are
mentioned subsequently solely for explanatory purposes.

```{r k3-category-mix}
# Checking how the video categories are being distributed across the 3 clusters.
# The categories are only being used for comparison and not for creating the clusters.
round(
  prop.table(
    table(K3$cluster, cluster_categories),
    1
  ),
  3
)
```

Cluster 1 represents a large mixed cluster that encompasses comments
from all three categories, with Career Mode comprising 39.0%, Ultimate
Team 34.5%, and Review 26.6%.

Cluster 2 consists solely of comments from the Ultimate Team category.
The absence of label information for k-means suggests that the use of
pack-specific terminology effectively characterises the text within this
cluster.

Cluster 3 is mostly filled with comments from the Review category,
accounting for 64.8%. While this does not imply complete separation, it
demonstrates that the broader Review vocabulary discussed in Section 2.3
is also evident in the unsupervised clustering.

The mean TF-IDF weight of each term was then calculated for each
cluster.

```{r k3-terms}
# Looking at the TF-IDF values to find the most important terms in each cluster.
for (cluster_number in 1:3) {
  ids = which(K3$cluster == cluster_number)

  # Calculating the average TF-IDF weight for each term in the cluster.
  weights = colMeans(clustering.matrix[ids, ])

  # Displaying the 10 terms with the highest average weights for each cluster.
  cat("\nCluster", cluster_number, "\n")
  print(sort(weights, decreasing = TRUE)[1:10])
}
```

**Cluster 1 - Discussion Involving Both Players and General Topics.**\
This cluster is the most extensive, containing terms such as `pepe`,
`lucio`, `goat`, `love`, `good`, `buy`, `chelsea`, and `pirlo`. The
balance of categories and the diverse vocabulary utilised suggest that
this cluster deals with broad discussions, player mentions, and
reactions rather than a specific topic.

**Cluster 2 - Ultimate Team Pack Discussion.**\
This cluster comprises comments related to Ultimate Team. The most
interpretable terms within it are `pack`, `icon`, and `ultim`, which
clearly convey the concept of Ultimate Team packs. There are additional
highly weighted stems that lack meaning without context, leading us to
designate the cluster name based on the most interpretable terms.

**Cluster 3 - Review and Gameplay Discussion.**\
This cluster predominantly consists of review comments and includes
terms such as `fifa`, `play`, `look`, `year`, `football`, `efootball`,
and `feel`.

```{r k3-plot, fig.width=6.5, fig.height=3.2, out.width='60%'}
# Plotting the MDS points in two dimensions to see how the three clusters are being separated.
# Using different colours to show which cluster each point belongs to.
plot(
  mds2.matrix,
  col = K3$cluster,
  pch = 16,
  xlab = "MDS dimension 1",
  ylab = "MDS dimension 2",
  main = "Three-cluster solution"
)

# Adding a legend to make it easier to identify each cluster in the plot.
legend(
  "topright",
  legend = c("Cluster 1", "Cluster 2", "Cluster 3"),
  col = 1:3,
  pch = 16,
  cex = 0.8
)
```

The 2D MDS plot shows a substantial overlapping group, along with two
other branches that are more distinct. This aligns with the numerical
results, as most comments fall into a broad mixed cluster, while the
pack-related and review/gameplay clusters are more specific.

Therefore, we cannot view the cluster formation as the creation of a
distinct set of three thematic categories. The Ultimate Team pack
cluster stands out as the most noticeable. Following that, the
Review/gameplay cluster is also visible, although it is less distinct
than the Ultimate Team pack cluster. Our text analysis showed vocabulary
linked to Career Mode, but this cluster did not emerge as a major one in
the three-cluster solution.

This is an important limitation of the analysis rather than a failure of
the method. Given the fact that comments are very short and include lots
of football-related vocabulary in common, it is unlikely to achieve
complete separation of topics. It means that the analysis implies the
existence of some specialized topics in the general discussion space
related to the FC 27 launch.

Some other limitations of this analysis are its dependence on the
earlier cleaning steps and TF-IDF procedure, as well as the need to
remove 19 empty comments.

```{r network-setup, include=FALSE}
# Loading igraph for the network analysis.
library(igraph)

# Creating a function to convert unusual characters into simple text.
# This is helping to avoid problems with usernames when generating the PDF.
safe_ascii = function(x) {
  y = iconv(x, from = "", to = "ASCII//TRANSLIT", sub = "")
  y[is.na(y)] = ""
  y
}

# Cleaning the author names and creator names in the replies data.
replies$replyAuthor = safe_ascii(replies$replyAuthor)
replies$parentAuthor = safe_ascii(replies$parentAuthor)
replies$creator = safe_ascii(replies$creator)

# Cleaning the creator names and video titles in the selected videos.
# Channel IDs are still being used to identify users where available.
selected_videos$creator = safe_ascii(selected_videos$creator)
selected_videos$title = safe_ascii(selected_videos$title)
```

# 2.5 Network Analysis

The last portion of the research focuses on who **talks to whom** in the
chosen FC 27 discussions on YouTube.

This network analysis is founded on the actual replies collected within
the same 72-hour periods as in previous sections. Each node represents a
YouTube user, with a directed edge $A \rightarrow B$ indicating that
user A responded to a top-level comment made by user B.

This directional orientation is very important, as it allows for
distinct interpretations of in-degree and out-degree. A high in-degree
signifies that a considerable number of users have replied to that
particular user, while a high out-degree indicates that the user has
engaged with numerous other top-level commenters.

## Creating the list of edges for replies

We used YouTube channel IDs as the primary identifiers for users, given
their greater persistence compared to display names. In instances where
an ID was unavailable, we employed the public display name as a
substitute.

```{r network-ids}
# Using channel IDs to identify users even if their display names change.
# When a channel ID is missing, the username is being used instead.
reply_from = ifelse(
  is.na(replies$replyAuthorChannelId) | replies$replyAuthorChannelId == "",
  replies$replyAuthor,
  replies$replyAuthorChannelId
)

# Applying the same process to identify the users receiving the replies.
# Display names are also being kept separately to help identify users in the network.
reply_to = ifelse(
  is.na(replies$parentAuthorChannelId) | replies$parentAuthorChannelId == "",
  replies$parentAuthor,
  replies$parentAuthorChannelId
)
```

We removed records with a missing endpoint. Additionally, we excluded
self-replies, as an edge from a user to themselves does not signify
interaction between two distinct users.

```{r edge-data}
# Combining the reply users and video details into one table for the network analysis.
network_data = data.frame(
  from = reply_from,
  to = reply_to,
  replyAuthor = replies$replyAuthor,
  parentAuthor = replies$parentAuthor,
  videoId = replies$videoId,
  category = replies$category,
  creator = replies$creator,
  stringsAsFactors = FALSE
)

# Removing replies where either user cannot be identified.
# This is keeping only the replies with valid users on both sides.
network_data = network_data[
  !is.na(network_data$from) &
  !is.na(network_data$to) &
  network_data$from != "" &
  network_data$to != "",
]

# Removing replies where both users have the same identifier.
network_data = network_data[
  network_data$from != network_data$to,
]

# Checking how many reply records are remaining after cleaning.
nrow(network_data)
```

From the total of 480 replies collected, we obtained **436 usable
non-self replies** following the above filtering process.

Some users provided multiple responses to the same individual. In
constructing the graph, we merged multiple A-to-B relationships into a
single relationship to ensure that the degree reflected the number of
unique user contacts rather than the total number of replies.

```{r full-edge-list}
# Keeping only one reply connection for each pair of users.
# This is avoiding repeated replies from affecting the degree centrality results.
full_edges = unique(
  network_data[, c("from", "to")]
)

# Checking the number of rows and columns in the final edge list.
dim(full_edges)
```

The 436 usable reply events became **401 unique directed user-to-user
ties**.

## Full reply network

The full graph combines reply relationships from all nine selected
videos.

```{r author-lookup}
# Creating a lookup table to match channel IDs with readable usernames.
# Keeping the usernames separately so the network results are easier to understand.
author_lookup = rbind(
  data.frame(
    id = network_data$from,
    label = network_data$replyAuthor,
    stringsAsFactors = FALSE
  ),
  data.frame(
    id = network_data$to,
    label = network_data$parentAuthor,
    stringsAsFactors = FALSE
  )
)

# Removing repeated IDs and keeping the first username found for each user.
# Channel IDs are still being used as the main identifiers in the network.
author_lookup = author_lookup[
  !duplicated(author_lookup$id),
]
```

```{r full-graph}
# Creating a directed network using the unique reply connections between users.
g = graph_from_data_frame(
  full_edges,
  directed = TRUE
)

# Matching each user ID with their display name to make the network easier to read.
V(g)$display = author_lookup$label[
  match(V(g)$name, author_lookup$id)
]

# Using the original user ID when a display name is missing.
V(g)$display[
  is.na(V(g)$display)
] = V(g)$name[
  is.na(V(g)$display)
]

# Counting the users and connections in the network.
# Also calculating the network density to see how closely the users are connected.
data.frame(
  Nodes = vcount(g),
  Edges = ecount(g),
  Density = round(edge_density(g, loops = FALSE), 4)
)
```

The entire network has **492 nodes and 401 distinct edges**, and it has
a density value of **approximately 0.0017**. It is a very sparse
network, few of the possible user-to-user ties exist.

## Components

Since the network is a directed one, weak components are used to analyze
the connectivity among users if direction of edges is neglected.

```{r full-components}
# Checking how users are connected in the network without considering the direction of replies.
full_components = components(
  g,
  mode = "weak"
)

# Counting the separate groups and finding the size of the largest group.
# Also checking what proportion of users belong to the largest group.
# This is helping to understand how separated the network is.
data.frame(
  WeakComponents = full_components$no,
  LargestComponent = max(full_components$csize),
  LargestShare = round(
    max(full_components$csize) / vcount(g),
    3
  )
)
```

There are a total of **95 weakly connected components**. The largest
component comprises **66 individuals**, representing just **13.4%** of
all nodes.

This serves as clear evidence of the fragmentation within the reply
network. It indicates that there is not a singular, extensive dialogue
involving all participants,instead, we observe numerous distinct reply
chains and groups.

## Degree distribution

```{r degree-distribution}
# Calculating the total number of incoming and outgoing reply connections for each user.
full_degree = degree(
  g,
  mode = "all"
)

# Summarising the degree values to see how connections are being distributed among users.
summary(full_degree)

# Plotting the degree distribution to see how many users have fewer or more connections.
# This is helping to identify whether a small number of users have many connections.
hist(
  full_degree,
  breaks = 20,
  main = "Degree distribution of the full reply network",
  xlab = "Degree"
)
```

Median Degree is **1** and the Maximum Degree is **53.** The
distribution shows significant right skewness, indicating that the
majority of users have only one connection, whereas a minority of users
function as hubs.

This phenomenon is similarly observable in the reply network structure.
While numerous users engage in giving or receiving a single reply, those
who are either creators or highly active tend to receive or send a
greater number of replies.

## Visualisation of full-network

```{r full-network-plot, fig.width=7.5, fig.height=5.0, out.width='88%'}
# Counting the incoming, outgoing and total reply connections for each user.
full_in = degree(g, mode = "in")
full_out = degree(g, mode = "out")
full_degree = degree(g, mode = "all")

# Grouping users based on whether they are receiving or sending more replies.
# Users with the same number of incoming and outgoing connections are being marked as balanced.
node_type = ifelse(
  full_in > full_out,
  "More incoming",
  ifelse(
    full_out > full_in,
    "More outgoing",
    "Balanced"
  )
)

# Choosing different colours to show the three types of users in the network.
node_colours = c(
  "More incoming" = "lightblue",
  "More outgoing" = "orange",
  "Balanced" = "grey75"
)

# Assigning the colours to users based on their connection types.
plot_colours = unname(node_colours[node_type])

# Selecting the six most connected users to display their names on the graph.
# This is keeping the network plot from becoming too crowded.
full_labels = rep(NA, vcount(g))
top_label_ids = order(
  full_degree,
  decreasing = TRUE
)[1:min(6, vcount(g))]

full_labels[top_label_ids] = V(g)$display[top_label_ids]

# Setting the seed to keep the network layout consistent.
set.seed(3020)

# Plotting the reply network with node sizes based on the number of connections.
# The colours are showing the different reply patterns for each user.
plot(
  g,
  layout = layout_with_drl(g),
  vertex.size = 3 + sqrt(full_degree),
  vertex.color = plot_colours,
  vertex.label = full_labels,
  vertex.label.cex = 0.65,
  edge.arrow.size = 0.2,
  main = "Full FC 27 reply network"
)

# Adding a legend to explain what each node colour is representing.
legend(
  "topleft",
  legend = names(node_colours),
  col = node_colours,
  pch = 19,
  bty = "n",
  cex = 0.8
)
```

These properties are fully represented in the graph. Light blue nodes
have a greater number of unique ties directed towards them than those
they send, orange nodes show a higher number of unique ties sent than
received, while grey nodes are characterised by a balance. The majority
of the nodes are situated within small disconnected components, although
a few large hub-and-spoke clusters are observable.

## Centrality

There are two centrality metrics used for the **full graph**:

-   **Degree centrality** calculates the number of direct connections
    for each user.
-   **Betweenness centrality** calculates the number of shortest paths a
    user is located on, allowing for bridging opportunities within the
    sampled network.

Centrality is calculated on the entire network and not the smaller
subnetwork since the deletion of vertices would alter the paths and
scores.

```{r full-centrality}
# Creating a table to compare how connected each user is in the reply network.
centrality = data.frame(
  User = V(g)$display,

  # Counting how many replies are coming into and going out from each user.
  InDegree = degree(g, mode = "in"),
  OutDegree = degree(g, mode = "out"),

  # Calculating the total number of direct connections for each user.
  TotalDegree = degree(g, mode = "all"),

  # Checking how often each user is appearing between other users on directed shortest paths.
  Betweenness = betweenness(
    g,
    directed = TRUE
  ),
  stringsAsFactors = FALSE
)
```

## Highest Degree

```{r top-degree}
# Sorting the users by total degree to find the accounts with the most direct connections.
top_degree = centrality[
  order(
    centrality$TotalDegree,
    decreasing = TRUE
  ),
]

# Displaying the 10 most connected users in a table.
# Showing incoming and outgoing connections separately to see how each user is interacting in the network.
knitr::kable(
  head(
    top_degree[, c(
      "User",
      "InDegree",
      "OutDegree",
      "TotalDegree"
    )],
    10
  ),
  row.names = FALSE,
  caption = "Users with the highest degree centrality"
)
```

@AuzioMF has the greatest total degree which is **53** and all
in-degree. This implies that the account received incoming ties from 53
distinct users in the network and that the account did not generate any
outbound reply ties in this dataset.

@BFordLancer has the second highest total degree of **27** but the
pattern is different: 6 incoming ties and 21 outgoing ties. That means a
far more active involvement in responding to other commenters than just
getting replies.

## Highest Betweenness

```{r top-betweenness}
# Sorting the users by betweenness centrality to find those connecting different parts of the network.
top_betweenness = centrality[
  order(
    centrality$Betweenness,
    decreasing = TRUE
  ),
]

# Displaying the 10 users with the highest betweenness values.
# Also showing their total degree to compare their position in the network with their number of connections.
knitr::kable(
  head(
    top_betweenness[, c(
      "User",
      "TotalDegree",
      "Betweenness"
    )],
    10
  ),
  row.names = FALSE,
  caption = "Users with the highest betweenness centrality"
)
```

@BFordLancer displays the highest betweenness centrality, measured at
**130**. While @AuzioMF possesses numerous direct connections, it has a
betweenness centrality of zero,conversely, @BFordLancer plays a crucial
role in multiple directed paths among other users.

This distinction illustrates that each type of centrality addresses
different inquiries. Degree centrality identifies essential local nodes,
whereas betweenness centrality highlights positions akin to bridges.

## Choosing a Subgraph

The assignment also requires a justified smaller network. To avoid
choosing an easily visible network from the data set, we compared each
video's reply graph based on the number of nodes, edges, number of
components, and largest connected component.

```{r video-network-summary}
video_summary = data.frame()

for (video_id in selected_videos$videoId) {

  video_data = network_data[
    network_data$videoId == video_id,
  ]
  video_edges = unique(
    video_data[, c("from", "to")]
  )
  if (nrow(video_edges) == 0) {
    next
  }

  video_graph = graph_from_data_frame(
    video_edges,
    directed = TRUE
  )
  video_components = components(
    video_graph,
    mode = "weak"
  )
  video_summary = rbind(
    video_summary,
    data.frame(
      videoId = video_id,
      Nodes = vcount(video_graph),
      Edges = ecount(video_graph),
      Components = video_components$no,
      LargestComponent = max(video_components$csize),
      LargestShare = round(
        max(video_components$csize) /
        vcount(video_graph),
        3
      ),
      Density = round(
        edge_density(
          video_graph,
          loops = FALSE
        ),
        4
      )
    )
  )
}

video_summary = merge(
  video_summary,
  selected_videos[, c(
    "videoId",
    "creator",
    "category"
  )],
  by = "videoId"
)
video_summary = video_summary[
  order(
    video_summary$LargestComponent,
    decreasing = TRUE
  ),
]
video_summary_display = data.frame(
  Creator = video_summary$creator,
  Category = video_summary$category,
  Nodes = video_summary$Nodes,
  Edges = video_summary$Edges,
  Components = video_summary$Components,
  LargestComponent = video_summary$LargestComponent,
  LargestShare = paste0(
    round(video_summary$LargestShare * 100, 1),
    "%"
  ),
  stringsAsFactors = FALSE
)
knitr::kable(
  video_summary_display,
  row.names = FALSE,
  col.names = c(
    "Creator",
    "Category",
    "Nodes",
    "Edges",
    "Components",
    "Largest component",
    "Largest share"
  ),
  caption = "Reply-network structure by selected video"
)
```

The AuzioMF Ultimate Team video had the largest weakly connected
component, containing 66 users. Within the network for this video, there
are 100 users and 87 distinct edges, with the largest weak component
consisting of 66 users. In contrast, the BFordLancer video features a
largest component of 43 users, indicating that the AuzioMF discussion
represents the optimal choice for a connected subgraph. Notably, this is
the largest component within the entire combined network.

## Largest connected reply subgraph

```{r build-subgraph}
subgraph_video_id = video_summary$videoId[1]

video_data = network_data[
  network_data$videoId == subgraph_video_id,
]

video_edges = unique(
  video_data[, c("from", "to")]
)

video_graph = graph_from_data_frame(
  video_edges,
  directed = TRUE
)

video_components = components(
  video_graph,
  mode = "weak"
)

largest_component_number = which.max(
  video_components$csize
)

largest_component_vertices = V(video_graph)[
  video_components$membership ==
  largest_component_number
]

g_sub = induced_subgraph(
  video_graph,
  largest_component_vertices
)

V(g_sub)$display = author_lookup$label[
  match(V(g_sub)$name, author_lookup$id)
]
V(g_sub)$display[
  is.na(V(g_sub)$display)
] = V(g_sub)$name[
  is.na(V(g_sub)$display)
]
```

```{r subgraph-summary}
# Checking the number of users and reply connections in the selected subgraph.
# Also calculating the density to see how closely the users are connected.
data.frame(
  SubgraphNodes = vcount(g_sub),
  SubgraphEdges = ecount(g_sub),
  SubgraphDensity = round(
    edge_density(
      g_sub,
      loops = FALSE
    ),
    4
  )
)
```

The chosen connected sub-graph has **66 nodes and 66 directed edges**,
where density = **0.0154**. It is more connected compared than the
combined network, but it is still highly sparse.

```{r subgraph-plot, fig.width=7.5, fig.height=5.0, out.width='88%'}
# Counting the incoming, outgoing and total reply connections in the smaller network.
sub_in = degree(g_sub, mode = "in")
sub_out = degree(g_sub, mode = "out")
sub_degree = degree(g_sub, mode = "all")

# Grouping users based on whether they are receiving or sending more replies.
# Using the same groups as the full network to keep the colours consistent.
sub_type = ifelse(
  sub_in > sub_out,
  "More incoming",
  ifelse(
    sub_out > sub_in,
    "More outgoing",
    "Balanced"
  )
)

# Assigning the colours based on each user's reply connections.
sub_colours = unname(node_colours[sub_type])

# Selecting the six most connected users to display their names.
# This is keeping the smaller network easier to read.
sub_labels = rep(NA, vcount(g_sub))
sub_top_ids = order(
  sub_degree,
  decreasing = TRUE
)[1:min(6, vcount(g_sub))]

sub_labels[sub_top_ids] = V(g_sub)$display[sub_top_ids]

# Setting the seed to keep the graph layout consistent.
set.seed(3020)

# Plotting the largest connected group with node sizes based on total degree.
# Using the colours to show the different incoming and outgoing reply patterns.
plot(
  g_sub,
  layout = layout_with_fr(g_sub),
  vertex.size = 5 + sqrt(sub_degree) * 2,
  vertex.color = sub_colours,
  vertex.label = sub_labels,
  vertex.label.cex = 0.75,
  edge.arrow.size = 0.35,
  main = "Largest connected reply subgraph"
)

# Adding a legend to explain what each colour is showing.
legend(
  "topleft",
  legend = names(node_colours),
  col = node_colours,
  pch = 19,
  bty = "n",
  cex = 0.8
)
```

This subnetwork also demonstrates an obvious **hub-and-spoke
architecture with regard to @AuzioMF**. The light blue location of the
node indicates the large amount of incoming ties, while many orange
nodes located nearby have only outgoing ties in the form of replies.

The small branch shows that the network is not a complete star, since
some users reply to other commenters and form chains, but not as often
as they reply to high-degree nodes.

## Interpretation and Limitations

The FC 27 reply network is large but fragmented, consisting of 492
users, 95 weakly connected components, and a network density of 0.0017.
Most users have only one connection, while a few accounts receive many
connections.

Centrality analysis identifies two key user types. @AuzioMF stands out
as the primary centre of the network, receiving numerous replies from
various users. @BFordLancer has fewer total ties than \@AuzioMF but much
higher betweenness, indicating a more bridge-like position on directed
shortest paths.

Several limitations exist. Firstly, the network depends on public reply
data from the YouTube API, excluding deleted, hidden, or inaccessible
comments. Additionally, YouTube comments are structured into top-level
comments, omitting multilevel discussions among individual replies. The
analysis is confined to the first 72 hours. The graph assesses various
interactions rather than the total number of messages sent, as repeated
interactions between the same users are condensed into a single
connection. Finally, the merging of nine videos into one graph results
in numerous disconnected components.

These limitations should be considered when examining the sparse network
structure with hubs. The network serves as a representation of reply
relationships in the early FC 27 debates, rather than a comprehensive
social network of the entire FC 27 community.

## 3. Overall Findings

Overall, the five stages indicate that the discourse surrounding the FC
27 launch is shaped by the type of content, yet it does not exist in
completely separate communities. We see differences in the themes of
discussion and interactions, but many elements of conversation are
common across all three categories.

The hypothesis test has shown strong evidence of differences in
interaction, with review comments having the highest likelihood of
receiving replies at 19.6%. In comparison, Ultimate Team and Career Mode
videos had reply rates of 13.3% and 10.8%, respectively. The chi-square
test indicated a general association between video category and the
presence of replies, with a statistic of $\chi^2(2)$ = 7.8272 and p =
0.01997. Although this does not establish causation, it highlights that
early interactions were not evenly distributed among the three content
types. Text analysis further clarifies some of these differences. Review
comments used more general language related to FIFA, football, gameplay,
and overall impressions. In contrast, Ultimate Team comments featured
more specific terms like "evos," "pack," and "market," while Career Mode
comments included words such as "sign," "career," "player," and
"Chelsea." These findings suggest that viewers responded to the video
content, but there are notable common vocabulary elements across the
different category groups.

Clustering analysis supports earlier conclusions while also highlighting
their limitations. The three-cluster solution included a large mixed
cluster with 534 comments, a small Ultimate Team pack cluster with 22
comments, and a Review/gameplay cluster with 145 comments. The pack
cluster was the most distinct, containing only Ultimate Team comments,
even though category labels were not used to construct the clusters.
Conversely, there was no prominent cluster for Career Mode comments, as
most remained in the mixed cluster. This suggests that while the content
category is associated with differences in the themes discussed, it does
not completely dictate the language used by commenters.

Network analysis provides an alternative perspective on the same
discourse. The reply network included 492 nodes and 401 ties, but its
density was just 0.0017, and there were 95 weak components. This
indicates that interaction is quite fragmented and does not form a
cohesive community discourse. The degree distribution was also highly
right-skewed, suggesting that most users have a very limited number of
ties. @AuzioMF recorded the highest total degree of 53, while
@BFordLancer achieved the highest betweenness centrality at 130. This
highlights that popularity and the role of an account as a bridge node
in the network are distinct concepts.

A valuable overall picture has emerged. Review comments had the highest
reply rate, while the most unique textual cluster came from Ultimate
Team videos. The reply network appeared as fragmented conversations with
several hubs. The Career Mode discussions displayed identifiable
vocabulary in the frequency analysis but were more integrated with the
larger mixed textual cluster. This suggests that the discourse
surrounding the launch of FC 27 is shaped by a combination of content
type and creator-based interaction.

## Overall Limitations

The conclusions must be taken into account when designing the project.
First of all, the 9 videos are not randomly sampled out of all FC 27
content, they are purposefully selected. Secondly, the period of the
first 72 hours after upload is analyzed. Finally, the balanced
720-comment sample is good for comparing categories but is not
applicable to representing the natural distribution of discussions on
YouTube. Indeed, YouTube commenters are self-selected people and might
differ from viewers who do not write any comments at all.

The results of the text analysis depend on the settings of text
processing such as custom stop-list, stemming, TF-IDF weighting, etc.

This one-word analysis does not account for the complexity of sarcasm or
even the overall phrase meaning. Moreover, some words can be specific to
the particular video or artist chosen. Comments in the chi-square
analysis are nested within nine videos, so independence may not hold
perfectly The results of clustering depend on how comments are
represented, the distance metric used, and the number of clusters k. In
the network analysis, repeated ties were collapsed and nine separate
videos were pooled into one graph. All these limitations mean that the
results describe the patterns in the initial FC 27 YouTube chat
discussion only, but not the entire community of FC 27 players.

On the other hand, similar results obtained through different approaches
imply that the content type is related to language used and interactions
in comments, but there is a particularly strong structure in special
discussions about the Ultimate Team and reply hubs initiated by the
authors of the comments.

**Repository:** `PASTE_GITHUB_OR_GITLAB_URL_HERE`
